Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex
conclusion fix

As future work, this study may be extended in many directions: analyze which
guidelines are more likely to be affected by security refactorings \Rui{?}\Sof{melhor?}; evaluate the impact
of each refactoring pattern on software maintainability \Rui{?}\Sof{}; investigate if there is
any correlation between software maintainability and popularity of the project; expand
our methodology with other software quality properties; validate these findings
with closed or private software; and, expand this analysis to other quality
standards.

>>>>

As future work, this study may be extended in many directions: analyze which
guidelines are more likely to be affected by security-related refactorings;
evaluate the impact of each refactoring pattern on software maintainability
\Rui{?}\Sof{}; investigate if there is any correlation between software
maintainability and popularity of the project; expand our methodology with other
software quality properties; validate these findings with closed or private
software; and, expand this analysis to other quality standards.
